---
title: "Project2"
author: "Yinzhou Zhu"
date: "6/29/2020"
output: 
  github_document:
    toc: true
params:
  day_of_week: "monday"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(caret)
library(gbm)
library(GGally)
library(parallel)
library(doParallel)
library(rmarkdown)
library(olsrr)
library(MuMIn)
```

# Preparations
Below are some custom functions that I will be using including data filtering and plotting.  
```{r functions}
convert_to_factors <- function(column_list) {
  popularity_data[column_list] <- lapply(popularity_data[column_list], factor)
  return(popularity_data)
}
filter_by_day <- function(day){
  day_data <- popularity_data %>% filter(select(popularity_data, contains(day))==1) %>% select(!contains("week") & !url & !timedelta)
  return(day_data)
}
box_plots <- function(var){
  base_plot <-ggplot(daily_data, aes(y = .data[[var]])) 
  base_plot + geom_boxplot()
}
box_plots_log <- function(var){
  base_plot <-ggplot(daily_data, aes(y = log(.data[[var]]))) 
  base_plot + geom_boxplot()
}
box_plots_2 <- function(var_1, var_2){
  base_plot <-ggplot(daily_data, aes(.data[[var_1]], log(.data[[var_2]]))) 
  base_plot + geom_boxplot(outlier.shape = NA) + geom_jitter(size = 0.2, width = 0.3, aes(colour = .data[[var_1]]))
}
density_plots <- function(var_1) {
  base_plot <-ggplot(daily_data, aes(.data[[var_1]]))
  base_plot + geom_density()
}
density_plots_log <- function(var_1) {
  base_plot <-ggplot(daily_data, aes(log(.data[[var_1]])))
  base_plot + geom_density()
}
get_lr_rmse <- function(fitted_model, test_values) {
  return(RMSE(fitted_model$fitted.values, test_values))
}
```

# Initial data exploration
## Data parsing and inspection
```{r data parsing and inspection}
popularity_data <- read.csv("OnlineNewsPopularity.csv")
anyNA(popularity_data)
str(popularity_data)
popularity_data <- convert_to_factors(c("data_channel_is_lifestyle", "data_channel_is_entertainment", "data_channel_is_bus", "data_channel_is_socmed", "data_channel_is_tech", "data_channel_is_world"))
```

## Partitioning data
Data filtering based on day of week and training/test data partitioning.  
```{r data partition}
daily_data <- filter_by_day(params$day_of_week)
set.seed(35)
partition_index <- createDataPartition(daily_data$shares,
              p = .8,
              list = FALSE,
              times = 1)
partition_index <- as.vector(partition_index)
train_data <- daily_data[partition_index, ]
test_data <- daily_data[-partition_index, ]
```

## Visualization
* 5-number summary  
* Density plot for `shares`  
* Boxplot for `shares`  
* Transformed density plot for `shares`  
* Transformed boxplot for `shares`  
* Comparison boxplots between different channels and share numbers  
* Correlation plot for predictors  
```{r initial data visualization}
summary(daily_data$shares)
density_plots("shares")
box_plots("shares")
density_plots_log("shares")
box_plots_log("shares")
box_plots_2("data_channel_is_lifestyle", "shares")
box_plots_2("data_channel_is_entertainment", "shares")
box_plots_2("data_channel_is_bus", "shares")
box_plots_2("data_channel_is_socmed", "shares")
box_plots_2("data_channel_is_tech", "shares")
box_plots_2("data_channel_is_world", "shares")
ggcorr(data = daily_data, size = 1, nbreaks = 5, method = c("everything", "pearson"))
```

## Linear regression model
* Step-wise forward+backward selection based on AIC values  
* AIC plot  
* Saved chosen predictors, training RMSE and test RMSE  
```{r linear model}
linear_model_fit <- lm(shares ~ ., data = train_data)
linear_model <- ols_step_both_aic(linear_model_fit)
linear_model
plot(linear_model$aic)
lr_formula <- paste0("shares ~ ", paste(linear_model$predictors, collapse = "+"))
final_linear_model <- lm(lr_formula, data = train_data)
lr_training_rmse <- get_lr_rmse(final_linear_model, train_data$shares)
lr_test_rmse <- get_lr_rmse(final_linear_model, test_data$shares)
lr_pred <- predict(final_linear_model, newdata = select(test_data, -"shares"))
head(lr_pred, 100)
```

## Non-linear regression model
* Random forests  
* Bagged tree  
* Boosting tree  
* Saved training RMSEs and test RMSEs  
```{r non-linear models}
cores <- 8
cl <- makePSOCKcluster(cores)
registerDoParallel(cl)
training_control <- trainControl(method = "repeatedcv", number = 10, repeats = 3, verboseIter = FALSE, allowParallel = TRUE)
set.seed(333)
rf_fit <- train(shares ~ ., train_data, method = "rf",
                preProcess=c("center", "scale"), trControl = training_control)
rf_fit

set.seed(333)
tree_bag_fit <- train(shares ~ ., train_data, method = "treebag",
                 preProcess=c("center", "scale"), trControl = training_control)
tree_bag_fit

set.seed(333)
bt_fit <- train(shares ~ ., train_data, method = "gbm", verbose = 0,
                preProcess=c("center", "scale"), trControl = training_control,
                tuneGrid = expand.grid(n.trees = c(100, 200, 500), interaction.depth = c(1,4,9),
                                       shrinkage = 0.1, n.minobsinnode = 10))
bt_fit

stopCluster(cl)
registerDoSEQ()

rf_train_pred <- predict(rf_fit, newdata = select(train_data, -"shares"))
rf_pred <- predict(rf_fit, newdata = select(test_data, -"shares"))
rf_train_rmse <- RMSE(rf_train_pred, test_data$shares)
rf_test_rmse <- RMSE(rf_pred, test_data$shares)

tb_train_pred <- predict(tree_bag_fit, newdata = select(train_data, -"shares"))
tb_pred <- predict(tree_bag_fit, newdata = select(test_data, -"shares"))
tb_train_rmse <- RMSE(tb_train_pred, test_data$shares)
tb_test_rmse <- RMSE(tb_pred, test_data$shares)

bt_train_pred <- predict(bt_fit, newdata = select(train_data, -"shares"))
bt_pred <- predict(bt_fit, newdata = select(test_data, -"shares"))
bt_train_rmse <- RMSE(bt_train_pred, test_data$shares)
bt_test_rmse <- RMSE(bt_pred, test_data$shares)
```

# Comparing models
```{r comparisons}
lr_performance <- c("Linear regression model", lr_training_rmse, lr_test_rmse)
rf_performance <- c("Random forests model", rf_train_rmse, rf_test_rmse)
tree_bag_performance <- c("Bagged tree model", tb_train_rmse, tb_test_rmse)
bt_performance <- c("Random forests model", bt_train_rmse, bt_test_rmse)
metric <- rbind(lr_performance, rf_performance, tree_bag_performance, bt_performance)
row.names(metric) <-NULL
kable(rbind(c("", "Training RMSE", "Test RMSE"), metric))
```

# Automating reports for each day of week
```{r automation, results='hide', echo=TRUE}
days <- c("monday", "tuesday", "wednesday", "thursday", "friday", "saturday", "sunday")

map(.x = days, .f = ~render(input = "template.Rmd",
                            output_file = paste0(.x,"_report.md"),
                            params = list(day_of_week = .x))
    )
```
The analysis for [Monday is available here](monday_report.md).  
The analysis for [Tuesday is available here](tuesday_report.md).  
The analysis for [Wednesday is available here](wednesday_report.md).  
The analysis for [Thursday is available here](thursday_report.md).  
The analysis for [Friday is available here](friday_report.md).  
The analysis for [Saturday is available here](saturday_report.md).  
The analysis for [Sunday is available here](sunday_report.md).  
